---
title: "Phe"
author: "Chao Tang"
date: 'Report created: `r Sys.Date()`'
output: 
  html_document: 
    code_folding: "hide"
    toc: true
    toc_depth: 4
    toc_float: 
      collapsed: false
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval      = T, #在块中运行代码(default = TRUE)
                      highlight = T, #高亮显示
                      echo      = F, #是否在输出中包含源代码
                      tidy      = T, #是否整理代码
                      error     = T, #是否在输出中包含错误信息
                      warning   = F, #是否在输出中包含警告(default = TRUE)
                      message   = F, #是否在输出中包含参考的信息
                      cache.    = F)
```

```{r}
library(readABF)
library(data.table)
library(S4Vectors)
library(IRanges)
library(changepoint)
library(ggplot2)

KBins <- function(sig, minseglen1 = 100, minseglen2 = 10, pen.value = 1e-3) {
  ansmean1 <- suppressWarnings(changepoint::cpt.meanvar(sig, penalty = "None", method = "PELT", minseglen = minseglen1))
  Tab1 <- data.table(P = sig, B1 = rep(seq_len(nseg(ansmean1)), seg.len(ansmean1)))
  Tab2 <- Tab1[, .(P = median(P)), by = "B1"]
  
  ansmean2 <- suppressWarnings(changepoint::cpt.meanvar(Tab2[, P], penalty = "Asymptotic", pen.value = pen.value, method = "PELT", minseglen = minseglen2))
  Tab2[, B := rep(seq_len(nseg(ansmean2)), seg.len(ansmean2))]
  res <- merge(Tab1, Tab2[, .(B1, B)], by = "B1")
  res[, B1 := NULL]
  res[, .(P = median(P), N = .N), "B"][, rep(P, N)]
}

KBins2 <- function(sig, minseglen1 = 100, minseglen2 = 10, pen.value = 1e-3) {
  ansmean1 <- suppressWarnings(changepoint::cpt.mean(sig, penalty = "MBIC", method = "PELT", minseglen = minseglen1))
  Tab1 <- data.table(P = sig, B1 = rep(seq_len(nseg(ansmean1)), seg.len(ansmean1)))
  Tab2 <- Tab1[, .(P = median(P)), by = "B1"]
  
  ansmean2 <- suppressWarnings(changepoint::cpt.meanvar(Tab2[, P], penalty = "Asymptotic", pen.value = pen.value, method = "PELT", minseglen = minseglen2))
  Tab2[, B := rep(seq_len(nseg(ansmean2)), seg.len(ansmean2))]
  res <- merge(Tab1, Tab2[, .(B1, B)], by = "B1")
  res[, B1 := NULL]
  res[, .(P = median(P), N = .N), "B"][, rep(P, N)]
}
```

# Step1. read ABF file

```{r}
phe <- readABF::readABF("/mnt/raid62/Personal_data/zhangdan/AA_zhangming/0303-phe#1/21303003.abf")

phe <- as.data.table(as.data.frame(phe))
colnames(phe) <- c("Time", "pA", "mV")
```

Only keep data with a voltage of 50 mV
```{r}
paste0("Only ", round(mean(phe[, round(mV) == 50]) * 100, 2), "% of the data is retained.")
phe <- phe[round(mV) == 50, ]
```

Raw current density plot
```{r fig.width=12, fig.height=6}
plot(density(phe[pA < 130 & pA >= 0, pA], adjust = 3), xlab = "Current (pA)", main = "density of raw current")
```

# Step2. Noise reduction

```{r}
phe$Sm <- KBins(sig = phe$pA, pen.value = 1e-3, minseglen1 = 4, minseglen2 = 20)
# phe$Sm <- KBins2(sig = phe$pA, pen.value = 1-1e-3, minseglen1 = 4, minseglen2 = 2)
```

```{r fig.width=12, fig.height=6}
phe[Time > 0.91 & Time < 0.94, plot(Time, pA, type = "s")]
phe[Time > 0.91 & Time < 0.94, lines(Time, Sm, type = "s", col = "red")]
```

## Density plot of smoothed signal

```{r fig.width=12, fig.height=6}
DenSm <- density(phe[Sm < 130 & Sm >= 0, Sm], adjust = 3)

Bx <- DenSm$x[start(IRanges(diff(DenSm$y) > 0))]
By <- DenSm$y[start(IRanges(diff(DenSm$y) > 0))]

Px <- DenSm$x[start(IRanges(diff(DenSm$y) < 0))]
Py <- DenSm$y[start(IRanges(diff(DenSm$y) < 0))]

ic <- Py > 0.1 * max(Py)

plot(DenSm, xlab = "Current (pA)", main = "density of smooth current")
text(x = Px[ic], y = Py[ic] + max(Py) * 0.02, labels = round(Px[ic], 1))

ib <- c(mapply(Px[ic], FUN = function(x) max(which(Bx < x))), mapply(Px[ic], FUN = function(x) min(which(Bx > x))))
ib <- ib[!is.infinite(ib)]

text(x = Bx[ib], y = By[ib] - max(Py) * 0.02, labels = round(Bx[ib], 1))
```

# Step3. Division of signal interval

```{r}
L0 <- c(112.3, 120)
L1 <- c(88.5, 100.9)
L2 <- c(40, 88.5)
```

```{r}
phe[Sm > max(L0), L := "A"]
phe[Sm <= max(L0) & Sm > min(L0), L := "B"] # baseline
phe[Sm <= min(L0) & Sm > max(L1), L := "C"]
phe[Sm <= max(L1) & Sm > min(L1), L := "D"] # first
phe[Sm <= max(L2) & Sm > min(L2), L := "E"] # second
phe[Sm <= min(L2), L := "F"]
```

# Step4. Secondary baseline filtering

## Primary baseline signal

```{r}
LRle <- Rle(phe[, L])
LRg <- IRanges(start(LRle), end(LRle))
mcols(LRg)$L <- runValue(LRle)

LRleVa <- paste0(runValue(LRle), collapse = "")

L <- do.call(c, lapply(1:4, function(x) combn(LETTERS[3:6], x, simplify = F)))
R <- lapply(L, rev)

allcombn <- gtools::permutations(length(L), 2, repeats = T)
allcombn <- lapply(seq_len(nrow(allcombn)), function(i) {
  paste0("B", paste0(c(L[[allcombn[i, ][1]]], R[[allcombn[i, ][2]]]), collapse = ""), "B")
})
allcombn <- lapply(allcombn, function(x) paste0(runValue(Rle(unlist(strsplit(x, "")))), collapse = ""))
allcombn <- unique(allcombn)

BXB <- lapply(allcombn, function(x) gregexpr(x, LRleVa)[[1]])
BXB <- BXB[!mapply(function(x) all(x == -1), BXB)]

BXB <- lapply(BXB, function(x) {
  start <- as.numeric(x)
  steps <- unique(attr(x, "match.length"))
  sort(do.call(c, lapply(0:(steps - 1), function(x) start + x)))
})

BXB_Rg <- LRg[sort(unlist(BXB))]

fa <- findOverlaps(IRanges(start = seq_len(nrow(phe)), width = 1), BXB_Rg)

phe_BXB <- phe[queryHits(fa), ]
```

```{r}
LRle <- Rle(phe_BXB[, L])
LRg <- IRanges(start(LRle), end(LRle))
mcols(LRg)$L <- runValue(LRle)

LRleVa <- paste0(runValue(LRle), collapse = "")

L <- do.call(c, lapply(1:4, function(x) combn(LETTERS[3:6], x, simplify = F)))
R <- lapply(L, rev)

allcombn <- gtools::permutations(length(L), 2, repeats = T)
allcombn <- lapply(seq_len(nrow(allcombn)), function(i) {
  paste0("B", paste0(c(L[[allcombn[i, ][1]]], R[[allcombn[i, ][2]]]), collapse = ""), "B")
})
allcombn <- lapply(allcombn, function(x) paste0(runValue(Rle(unlist(strsplit(x, "")))), collapse = ""))

allcombn <- allcombn[mapply(function(x) sum(unlist(strsplit(x, "")) == "B") == 2, allcombn)]
allcombn <- unique(allcombn)

BXB <- lapply(allcombn, function(x) gregexpr(x, LRleVa)[[1]])
BXB <- BXB[!mapply(function(x) all(x == -1), BXB)]

BXB <- do.call(c, lapply(BXB, function(x) {
  start <- as.numeric(x)
  steps <- unique(attr(x, "match.length"))
  lapply(start, function(x) LRg[x:(x + steps - 1)])
}))

BXB <- lapply(BXB, function(x) {
  L_Flank <- tail(width(IRanges(phe_BXB[start(x[1]):end(x[1]), Sm] == tail(phe_BXB[start(x[1]):end(x[1]), Sm], 1))), 1)
  R_Flank <- head(width(IRanges(phe_BXB[start(x[length(x)]):end(x[length(x)]), Sm] == head(phe_BXB[start(x[length(x)]):end(x[length(x)]), Sm], 1))), 1)
  start(x[1]) <- end(x[1]) - L_Flank + 1
  end(x[length(x)]) <- start(x[length(x)]) + R_Flank - 1
  phe_BXB[min(start(x)):max(end(x)), ]
})
```

## Secondary baseline signal

```{r}
LRle <- Rle(phe[, L])
LRg <- IRanges(start(LRle), end(LRle))
mcols(LRg)$L <- runValue(LRle)

LRleVa <- paste0(runValue(LRle), collapse = "")

L <- do.call(c, lapply(1:5, function(x) combn(LETTERS[2:6], x, simplify = F)))
R <- lapply(L, rev)

allcombn <- gtools::permutations(length(L), 2, repeats = T)
allcombn <- lapply(seq_len(nrow(allcombn)), function(i) {
  paste0("A", paste0(c(L[[allcombn[i, ][1]]], R[[allcombn[i, ][2]]]), collapse = ""), "A")
})
allcombn <- lapply(allcombn, function(x) paste0(runValue(Rle(unlist(strsplit(x, "")))), collapse = ""))

allcombn <- allcombn[!mapply(function(x) sum(unlist(strsplit(x, "")) == "B") == 2, allcombn)]
allcombn <- unique(allcombn)

AXA <- lapply(allcombn, function(x) gregexpr(x, LRleVa)[[1]])
AXA <- AXA[!mapply(function(x) all(x == -1), AXA)]

AXA <- lapply(AXA, function(x) {
  start <- as.numeric(x)
  steps <- unique(attr(x, "match.length"))
  sort(do.call(c, lapply(0:(steps - 1), function(x) start + x)))
})

AXA_Rg <- LRg[sort(unlist(AXA))]

fa <- findOverlaps(IRanges(start = seq_len(nrow(phe)), width = 1), AXA_Rg)

phe_AXA <- phe[queryHits(fa), ]
```

```{r}
LRle <- Rle(phe_AXA[, L])
LRg <- IRanges(start(LRle), end(LRle))
mcols(LRg)$L <- runValue(LRle)

LRleVa <- paste0(runValue(LRle), collapse = "")

L <- do.call(c, lapply(1:5, function(x) combn(LETTERS[2:6], x, simplify = F)))
R <- lapply(L, rev)

allcombn <- gtools::permutations(length(L), 2, repeats = T)
allcombn <- lapply(seq_len(nrow(allcombn)), function(i) {
  paste0("A", paste0(c(L[[allcombn[i, ][1]]], R[[allcombn[i, ][2]]]), collapse = ""), "A")
})
allcombn <- lapply(allcombn, function(x) paste0(runValue(Rle(unlist(strsplit(x, "")))), collapse = ""))

allcombn <- allcombn[!mapply(function(x) sum(unlist(strsplit(x, "")) == "B") == 2, allcombn)]
allcombn <- unique(allcombn)

AXA <- lapply(allcombn, function(x) gregexpr(x, LRleVa)[[1]])
AXA <- AXA[!mapply(function(x) all(x == -1), AXA)]

AXA <- do.call(c, lapply(AXA, function(x) {
  start <- as.numeric(x)
  steps <- unique(attr(x, "match.length"))
  lapply(start, function(x) LRg[x:(x + steps - 1)])
}))

AXA <- lapply(AXA, function(x) {
  L_Flank <- tail(width(IRanges(phe_AXA[start(x[1]):end(x[1]), Sm] == tail(phe_AXA[start(x[1]):end(x[1]), Sm], 1))), 1)
  R_Flank <- head(width(IRanges(phe_AXA[start(x[length(x)]):end(x[length(x)]), Sm] == head(phe_AXA[start(x[length(x)]):end(x[length(x)]), Sm], 1))), 1)
  start(x[1]) <- end(x[1]) - L_Flank + 1
  end(x[length(x)]) <- start(x[length(x)]) + R_Flank - 1
  phe_AXA[min(start(x)):max(end(x)), ]
})

AXA <- AXA[mapply(function(x) any(x[, pA] < max(L1)), AXA)]
```

# Step5. Primary baseline current processing

## Repolish

```{r}
# BXB2 <- mclapply(BXB, function(x) {
#   y <- tryCatch(KBins2(sig = x[L != "B", pA], pen.value = 1 - 1e-2, minseglen1 = 4, minseglen2 = 2), error = function(e) NA)
#   if(is.na(y)) {
#     return(x)
#   } else {
#     x[L != "B", Sm := y]
#     return(x)
#   }
# }, mc.cores = 10)
BXB2 <- BXB
```

## Current density of primary baseline

```{r fig.width=12, fig.height=6}
DenSm <- density(do.call(rbind, BXB2)[Sm < 130 & Sm >= 0, Sm], adjust = 20)

Bx <- DenSm$x[start(IRanges(diff(DenSm$y) > 0))]
By <- DenSm$y[start(IRanges(diff(DenSm$y) > 0))]

Px <- DenSm$x[start(IRanges(diff(DenSm$y) < 0))]
Py <- DenSm$y[start(IRanges(diff(DenSm$y) < 0))]

ic <- Py > 0.01 * max(Py)

plot(DenSm, xlab = "Current (pA)", main = "density of smooth current")
text(x = Px[ic], y = Py[ic] + max(Py) * 0.02, labels = round(Px[ic], 1))

ib <- c(mapply(Px[ic], FUN = function(x) max(which(Bx < x))), mapply(Px[ic], FUN = function(x) min(which(Bx > x))))
ib <- ib[!is.infinite(ib)]

text(x = Bx[ib], y = By[ib] - max(Py) * 0.02, labels = round(Bx[ib], 1))
```

Remove the baseline
```{r fig.width=12, fig.height=6}
DenSm <- density(do.call(rbind, BXB2)[Sm < 130 & Sm >= 0 & L != "B", Sm], adjust = 0.7)

Bx <- DenSm$x[start(IRanges(diff(DenSm$y) > 0))]
By <- DenSm$y[start(IRanges(diff(DenSm$y) > 0))]

Px <- DenSm$x[start(IRanges(diff(DenSm$y) < 0))]
Py <- DenSm$y[start(IRanges(diff(DenSm$y) < 0))]

ic <- Py > 0.1 * max(Py)

plot(DenSm, xlab = "Current (pA)", main = "density of smooth current")
text(x = Px[ic], y = Py[ic] + max(Py) * 0.02, labels = round(Px[ic], 1))

ib <- c(mapply(Px[ic], FUN = function(x) max(which(Bx < x))), mapply(Px[ic], FUN = function(x) min(which(Bx > x))))
ib <- ib[!is.infinite(ib)]

text(x = Bx[ib], y = By[ib] - max(Py) * 0.02, labels = round(Bx[ib], 1))
```

```{r}
L1 <- c(87, 98)
```

Remove the level1
```{r fig.width=12, fig.height=6}
DenSm <- density(do.call(rbind, BXB2)[Sm < min(L1), Sm], adjust = 0.3)

Bx <- DenSm$x[start(IRanges(diff(DenSm$y) > 0))]
By <- DenSm$y[start(IRanges(diff(DenSm$y) > 0))]

Px <- DenSm$x[start(IRanges(diff(DenSm$y) < 0))]
Py <- DenSm$y[start(IRanges(diff(DenSm$y) < 0))]

ic <- Py > 0.3 * max(Py)

plot(DenSm, xlab = "Current (pA)", main = "density of smooth current")
text(x = Px[ic], y = Py[ic] + max(Py) * 0.02, labels = round(Px[ic], 1))

ib <- c(mapply(Px[ic], FUN = function(x) max(which(Bx < x))), mapply(Px[ic], FUN = function(x) min(which(Bx > x))))
ib <- ib[!is.infinite(ib)]

text(x = Bx[ib], y = By[ib] - max(Py) * 0.02, labels = round(Bx[ib], 1))
```

```{r}
L2 <- c(75.5, 81)
```

Remove the level2
```{r fig.width=12, fig.height=6}
DenSm <- density(do.call(rbind, BXB2)[Sm < min(L2), Sm], adjust = 0.5)

Bx <- DenSm$x[start(IRanges(diff(DenSm$y) > 0))]
By <- DenSm$y[start(IRanges(diff(DenSm$y) > 0))]

Px <- DenSm$x[start(IRanges(diff(DenSm$y) < 0))]
Py <- DenSm$y[start(IRanges(diff(DenSm$y) < 0))]

ic <- Py > 0.1 * max(Py)

plot(DenSm, xlab = "Current (pA)", main = "density of smooth current")
text(x = Px[ic], y = Py[ic] + max(Py) * 0.02, labels = round(Px[ic], 1))

ib <- c(mapply(Px[ic], FUN = function(x) max(which(Bx < x))), mapply(Px[ic], FUN = function(x) min(which(Bx > x))))
ib <- ib[!is.infinite(ib)]

text(x = Bx[ib], y = By[ib] - max(Py) * 0.02, labels = round(Bx[ib], 1))
```

```{r}
L3 <- c(59.7, 66.8)
L4 <- c(46.6, 55.1)
```

```{r fig.width=12, fig.height=6}
DenSm <- density(do.call(rbind, BXB2)[Sm < max(L1), Sm], adjust = 0.6)

Bx <- DenSm$x[start(IRanges(diff(DenSm$y) > 0))]
By <- DenSm$y[start(IRanges(diff(DenSm$y) > 0))]

Px <- DenSm$x[start(IRanges(diff(DenSm$y) < 0))]
Py <- DenSm$y[start(IRanges(diff(DenSm$y) < 0))]

ic <- Py > 0.02 * max(Py)

plot(DenSm, type = "l", xlab = "Current (pA)", main = "density of smooth current")
text(x = Px[ic], y = Py[ic] + max(Py) * 0.02, labels = round(Px[ic], 1))
```

## Signal classification

```{r}
BXB2 <- BXB2[mapply(function(x) any(x[, Sm] < max(L1)), BXB2)]
```

```{r}
BXB2 <- lapply(BXB2, function(x) {
  x[, L := NULL]
  x[Sm <= max(L0) & Sm > min(L0), L := "B"] # baseline
  x[Sm <= max(L1) & Sm > min(L1), L := "1"] # first
  x[Sm <= max(L2) & Sm > min(L2), L := "2"] # second
  x[Sm <= max(L3) & Sm > min(L3), L := "3"] # third
  x[Sm <= max(L4) & Sm > min(L4), L := "4"] # fourth
  return(x)
})
```

## Filtering

```{r}
BXB2 <- BXB2[!mapply(function(x) all(unique(x[!is.na(L), L]) == "B"), BXB2)]
```

```{r}
Lsd <- mapply(function(x) x[!is.na(L) & L != "B", sd(pA), by = "L"][, mean(V1)], BXB2)
BXB2 <- BXB2[Lsd < quantile(Lsd, .95)]
```

```{r}
Lna <- mapply(function(x) x[, mean(is.na(L))], BXB2)
BXB2 <- BXB2[Lna < .05]
```

```{r}
Lna <- mapply(function(x) x[, sum(is.na(L))]/x[L != "B" | is.na(L), .N], BXB2)
BXB2 <- BXB2[Lna < .05]
```

```{r}
mapply(BXB2, FUN = function(x) {
  paste0(runValue(Rle(x[!is.na(L), L])), collapse = "")
}) -> sigclass
names(BXB2) <- sigclass
```

```{r}
sigclass <- as.data.table(as.data.frame(table(sigclass), stringsAsFactors = FALSE))
sigclass[, sigclass := as.character(sigclass)]
# sigclass[, sigclass := gsub("^B", "", sigclass)]
# sigclass[, sigclass := gsub("B$", "", sigclass)]

setkey(sigclass, Freq, sigclass)
sigclass$sigclass <- factor(sigclass$sigclass, levels = rev(sigclass$sigclass))
```

```{r fig.width=10, fig.height=4}
ggplot(sigclass, aes(x = sigclass, y = Freq)) + 
  geom_col() + 
  geom_text(aes(x = sigclass, y = Freq + 30, label = Freq)) +
  theme_classic(base_size = 15) + 
  theme(axis.title.x = element_blank()) + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

## Example of primary baseline

```{r fig.width=12, fig.height=6}
Tab <- BXB2[[which(names(BXB2) == "B14B")[1]]]
Tab <- BXB2[[which(names(BXB2) == "B1B")[118]]]
Tab <- BXB2[[61]]

ggplot() + 
  geom_step(data = Tab, aes(Time, pA)) + 
  geom_step(data = Tab, aes(Time, Sm, colour = "red")) + 
  geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = min(L0), ymax = max(L0)), alpha = 0.2) + 
  geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = min(L1), ymax = max(L1)), alpha = 0.2) + 
  geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = min(L2), ymax = max(L2)), alpha = 0.2) + 
  geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = min(L3), ymax = max(L3)), alpha = 0.2) + 
  geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = min(L4), ymax = max(L4)), alpha = 0.2) + 
  theme_classic(base_size = 16) + 
  theme(legend.position = "none")
```


```{r}
saveRDS(object = BXB2, file = "/mnt/raid61/Personal_data/tangchao/AANanopore/analysis/01.AASignalRecognition/ZhangMing20210402/phe/21303003_BXB.Rds")
```

# Step6. Secondary baseline signal

```{r fig.width=12, fig.height=6}
Tab <- AXA[[21]]

ggplot() + 
  geom_step(data = Tab, aes(Time, pA)) + 
  geom_step(data = Tab, aes(Time, Sm, colour = "red")) + 
  geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = min(L0), ymax = max(L0)), alpha = 0.2) + 
  geom_rect(aes(xmin = -Inf, xmax = Inf, ymin = min(L1), ymax = max(L1)), alpha = 0.2) + 
  theme_classic(base_size = 16) + 
  theme(legend.position = "none")
```

## Current density of secondary baseline

```{r fig.width=12, fig.height=6}
DenSm <- density(do.call(rbind, AXA)[Sm < 130 & Sm >= 0, Sm], adjust = 3)

Bx <- DenSm$x[start(IRanges(diff(DenSm$y) > 0))]
By <- DenSm$y[start(IRanges(diff(DenSm$y) > 0))]

Px <- DenSm$x[start(IRanges(diff(DenSm$y) < 0))]
Py <- DenSm$y[start(IRanges(diff(DenSm$y) < 0))]

ic <- Py > 0.1 * max(Py)

plot(DenSm, xlab = "Current (pA)", main = "density of smooth current")
text(x = Px[ic], y = Py[ic] + max(Py) * 0.02, labels = round(Px[ic], 1))

ib <- c(mapply(Px[ic], FUN = function(x) max(which(Bx < x))), mapply(Px[ic], FUN = function(x) min(which(Bx > x))))
ib <- ib[!is.infinite(ib)]

text(x = Bx[ib], y = By[ib] - max(Py) * 0.02, labels = round(Bx[ib], 1))
```

Remove the baseline
```{r fig.width=12, fig.height=6}
DenSm <- density(do.call(rbind, AXA)[Sm < 130 & Sm >= 0 & L != "A", Sm], adjust = 3)

Bx <- DenSm$x[start(IRanges(diff(DenSm$y) > 0))]
By <- DenSm$y[start(IRanges(diff(DenSm$y) > 0))]

Px <- DenSm$x[start(IRanges(diff(DenSm$y) < 0))]
Py <- DenSm$y[start(IRanges(diff(DenSm$y) < 0))]

ic <- Py > 0.1 * max(Py)

plot(DenSm, xlab = "Current (pA)", main = "density of smooth current")
text(x = Px[ic], y = Py[ic] + max(Py) * 0.02, labels = round(Px[ic], 1))

ib <- c(mapply(Px[ic], FUN = function(x) max(which(Bx < x))), mapply(Px[ic], FUN = function(x) min(which(Bx > x))))
ib <- ib[!is.infinite(ib)]

text(x = Bx[ib], y = By[ib] - max(Py) * 0.02, labels = round(Bx[ib], 1))
```

